Tropical Andes Taxonomic Diversity of Plants and Frugivores

### 2024-05-22 code/L2/L2_1_TropicalAndes_taxdiv.Rmd
modify richness function to iteratively calculate richness if TAGrid has more than 1000 rows

  # Calculate cell richness for plants
  plant_richness_grid <- TAGrid %>%
    st_join(plants_sf_species) %>%
    mutate(overlap = ifelse(!is.na(species), 1, 0)) %>%
    group_by(cellid) %>%
    summarize(num_species = sum(overlap))

  # Calculate cell richness for frugivores
  frugivore_richness_grid <- TAGrid %>%
    st_join(frugivores_sf_species) %>%
    mutate(overlap = ifelse(!is.na(species), 1, 0)) %>%
    group_by(cellid) %>%
    summarize(num_species = sum(overlap))

>>>>

  # Function to calculate richness for a given dataset
  calculate_richness <- function(data_sf, species_sf) {
    result <- data_sf %>%
      st_join(species_sf) %>%
      mutate(overlap = ifelse(!is.na(species), 1, 0)) %>%
      group_by(cellid) %>%
      summarize(num_species = sum(overlap)) %>%
      ungroup()
    return(result)
  }

  # Determine the chunk size
  chunk_size <- 1000

  # Split the TAGrid into chunks if necessary
  TAGrid_chunks <- split(TAGrid, ceiling(seq_along(TAGrid$cellid) / chunk_size))

  # Initialize empty data frames for results
  plant_richness_grid <- list()
  frugivore_richness_grid <- list()

  # Iterate over chunks to calculate richness
  for (i in seq_along(TAGrid_chunks)) {
    chunk <- TAGrid_chunks[[i]]

    # Debug: Print chunk info
    print(paste("Processing chunk", i, "of", length(TAGrid_chunks)))

    plant_richness_chunk <- calculate_richness(chunk, plants_sf_species)
    frugivore_richness_chunk <- calculate_richness(chunk, frugivores_sf_species)

    # Store the chunks in lists
    plant_richness_grid[[i]] <- plant_richness_chunk
    frugivore_richness_grid[[i]] <- frugivore_richness_chunk
  }

  # Combine all chunks into final data frames
  plant_richness_grid <- bind_rows(plant_richness_grid)
  frugivore_richness_grid <- bind_rows(frugivore_richness_grid)
